---
pagetitle: documentation
---
```{r child='assets/setup.Rmd'}
```

```{r echo=FALSE}
menuNavbar()
```

```{r includeDT, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(htmltools)
library(tidyr)
library(magrittr)
library(shinydashboard)
library(DT)
library(htmltools)
library(magrittr)
library(shinydashboard)
library(shiny)
library(purrr)
library(DT)
library(here)
htmltools::tagList(
  rmarkdown::html_dependency_font_awesome(),
  rmarkdown::html_dependency_bootstrap(theme = "default"),
  rmarkdown::html_dependency_highlightjs(highlight = "default"))
##source(here("pages", "assets", "helpers.R"))
##htmltools::includeScript(here("pages", "assets", "custom.js"))
```

```{r echo=FALSE}
htmltools::tagList(
  rmarkdown::html_dependency_font_awesome(),
  rmarkdown::html_dependency_bootstrap(theme = "default"),
  rmarkdown::html_dependency_highlightjs(highlight = "default"))
htmltools::includeScript(here("pages", "assets", "custom.js"))

display_name <- function(fields) {
    sp <- gsub("_", " ", fields)
    paste0(toupper(substring(sp, 1, 1)), substring(sp, 2))
}
```

<div style="margin-left:100px; margin-right:100px; margin-top:10px;">

# Documentation

## {.tabset .nav-tabs-custom}

### Overview

#### Overview
MetaVoice is a research tool, bridging the gap between research fields investigating voice patterns in different (neuro)psychiatric disorders. At the moment, MetaVoice contains studies on voice patterns within `r length(unique(dataset_info$domain))` domains: `r display_name(unique(dataset_info$domain))`. Across these domains, there are currently `r as.integer(sum(as.numeric(dataset_info$num_experiments), na.rm = TRUE))` effect sizes from `r as.integer(sum(as.numeric(dataset_info$num_papers), na.rm = TRUE))` papers, including `r as.integer(sum(as.numeric(dataset_info$num_subjects), na.rm = TRUE))` subjects.

These aggregated data help to acquire better estimates of effect sizes across disorders, languages of participants and experimental methods. Thereby, it also becomes possible to explore the impact of potential moderators. The power analysis tool allows researchers to plan future studies with adequate sample sizes.

Learn more about the background of this page in “Reports - Our Bachelor’s Project”. 
<br/><br/>

#### Documentation 
+ For more information about individual datasets, see the `Datasets` tab.
+ For information about our statistical approach throughout the site, see the `Statistical Approach` tab.
+ For information about the field structure of the site, see the `Field Specification` tab. 
+ For information about doing meta-analyses and contributing to MetaVoice, see the `Contributing to MetaVoice` tab.
+ For information about how to download and cite data from MetaVoice, see the `Export Data` tab.
+ For more information about meta-analyses, see the `Meta-Analyses` tab.
<br/><br/>

#### Caveat

Please note that data and visualisations are under development at the moment (Autumn 2020) and should not be taken as definitive.


### Datasets

#### Datasets

On this page you can find all the datasets currently available on the MetaVoice website divided by domain (`r display_name(unique(dataset_info$domain))`). By clicking on the links, more information about the datasets can be found.


```{r results='asis', echo=FALSE}

display_name <- function(fields) {
    sp <- gsub("_", " ", fields)
    paste0(toupper(substring(sp, 1, 1)), substring(sp, 2))
}

domain <- ""

ret <- ""
for (i in 1:nrow(dataset_info)) {
  dataset <- dataset_info[i,]
  
  if (domain != dataset$domain) {
    domain <- dataset$domain
    ret <- paste(ret, sprintf("\n <h5> %s </h5>\n\n", display_name(domain)))
  }
  
  ret <- paste(ret, sprintf("<h6> [%s](/dataset/%s.html) \n\n * Citation: %s \n\n * N papers = %s, N effect sizes = %s \n\n * %s \n\n * Curator: %s \n\n * Comments: %s \n\n",
                            dataset$name, dataset$short_name, dataset$full_citation, dataset$num_papers, dataset$num_experiments, dataset$description, dataset$curator, dataset$comment))
}
cat(ret)
```

### Contributing to MetaVoice 

#### You would like to contribute to MetaVoice?

First of all, thank you for your support and your wish to contribute to MetaVoice. 

There are several ways in which you can contribute to the website and its contents. In general, you are always welcome to suggest new data and/or ideas for the website. Moreover, you are also more than welcome to join our team. Please see below, and [contact us](/about.html) if you are interested in contributing.
<br/><br/>

#### Ways of contributing:
- *Suggest and/or add data to an existing meta-analysis on the website:*<br/>
If you find or have conducted a study related to the field of voice patterns in (neuro)psychiatric disorders, which is not yet available on the MetaVoice website, you can suggest it as an addition to an already existing meta-analysis. This applies to data from both published and unpublished papers.
How: Email the curator of the existing meta-analysis with information on the study you found, and preferably include a link to or a pdf of the full text. This also applies if you are the author of the study. Ideally (but not necessarily), make the data fit the [MA template] (https://docs.google.com/spreadsheets/ - find the right link (make a template)), or make sure that the necessary data are provided in the email. From here, we will let you know how we/you can add the data to the existing meta-analysis.

- *Suggest and/or add a new meta-analysis:*\
If you find or have conducted a meta-analysis within the field of voice patterns in (neuro)psychiatric disorders, which is not yet available on the MetaVoice website, you can suggest this as a new meta-analysis within the particular domain. If your meta-analysis is related to a new domain see *Suggest a new domain to be added* below.
How: Email one of the team members with information on the meta-analysis, and preferably include a link to or a pdf of the full text (if published), or make sure that information about the data and the data itself is provided in the email (if unpublished). Ideally (but not necessarily), make the data fit the [MA template](https://docs.google.com/spreadsheets/ - find the right link (make a template)).

- *Create a new meta-analysis:*
If you want to contribute by creating your own meta-analysis, please see the [tutorial](http://metalab.stanford.edu/documentation/using_ma_data/) on the MetaLab website. This page will guide you through the different steps of creating a meta-analysis. Be aware that the tutorial page was created based on the field of cognitive development research, rather than voice patterns in (neuro)psychiatric disorders. Therefore, the [MA template for voice patterns in (neuro)psychiatric disorders](https://docs.google.com/spreadsheets/ - find the right link (make a template)), and the `Field specifications` for voice patterns in (neuro)psychiatric disorders](link) should be used when creating a meta-analysis within this field.

- *Suggest a new domain to be added:*
If you have an idea of a domain to be added within the field of voice patterns in (neuro)psychiatric disorders, you can contribute by suggesting this domain to us.
How: Email one of the team members with your suggestion, including the relevance of the domain and possible meta-analyses related to that domain. Please include a link to or a pdf of the full text(s), and we will get back to you.

- *Join us - become a curator:*
You can join our team by becoming a curator, helping maintain and update the website. Specifically, this means that you are responsible for:
    - Identifying new relevant data/papers by e.g. setting alerts for new papers on the meta-analysis topic.
    - Occasionally, checking data entry and correcting it if needed.
    - Determining which moderators should be displayed.

    As a curator, you will receive an email once a year, listing all of the meta-analyses which you are responsible for, and asking you whether you will continue to be a curator.

- *Suggest website features:*
If you want to contribute to the website by adding new features, or have other good ideas, you can let us know through [github](https://github.com/LNJ-ND/MetaVoice_Website) or [contact](/about.html) one of the team members. Please make it clear, what you would change, and how you would implement this.

- *Replicate the website within your own field of interest:*
Another way in which you can contribute, is by advocating the underlying aim of the website. That is, promoting a framework emphasising open science, open code, the importance of cumulative science, etc. You can do this by replicating the website within your own field of interest, and thereby make cumulative science more open and accessible in your field.
For a tutorial/instructions on how to replicate the website, see [replication of MetaVoice](LINK? To be created).
<br/><br/>

#### Ownership of data
If you have contributed with a meta-analysis of which you are the author, you might have some questions regarding the ownership of your data. Even though your meta-analysis is added to the webpage, you remain the owner of your meta-analysis data. Therefore, researchers using data from MetaVoice have to cite the publications related to your meta-analysis.



### Statistical Approach

#### Overview

All analyses on the site are conducted with the [`metafor`](http://www.metafor-project.org/doku.php) package (Viechtbauer, 2010). 
<br/><br/>

#### Effect Size Computation

Effect size computation is handled by a function called `mv_compute_es`, which can be found in the script mv_functions.R(https://github.com/LNJ-ND/MetaVoice_Website/blob/master/mv_functions.R). This function is based on a script [`compute_es.R`](https://github.com/langcog/metalab2/blob/master/scripts/compute_es.R), which has been developed by MetaLab. MetaLab cites [Hedges & Olkin's textbook](http://www.amazon.com/Statistical-Methods-Meta-Analysis-Larry-Hedges/dp/0123363802) as providing most of the formulas in the script. 
<br/><br/>

#### Statistical Models

The visualisations page uses a multi-level random effects model to conduct the meta-analyses ( `rma.mv` function of `metafor`).
Random-effect models allow for variability between studies and unique data points. To be specific, in our models a random intercept was defined for each sample (group of participants), since data from the same sample can be expected to be more similar than from a different sample. Further, a random intercept for each study was added, as data from the same study can be expected to be more similar than from a different study. This, thereby also accounts for cases in which the same sample contributed to data in two different studies.

The meta-analytic models are accessible in the script [`server.R`](https://github.com/LNJ-ND/MetaVoice_Website/blob/master/shinyapps/visualization/server.R)



### Field Specifications

#### Field Specifications
MetaVoice aims to follow open science practices, and the related FAIR principles (Reference). Therefore, all of the datasets used on this website can be downloaded. Working with unknown datasets can be challenging. The following information is supposed to help you understand the metavoice dataset.

This page gives the full specification for each field in the metavoice dataset, including: required fields (which must be included for every MA), optional fields (which are only used for some MAs), and derived fields (which are computed by the site).
<br/><br/>

```{r echo=FALSE, warning=FALSE, message=FALSE}

fields <- yaml::yaml.load_file(here("metadata", "spec.yaml"))
fields_derived <- yaml::yaml.load_file(here("metadata", "spec_derived.yaml")) %>%
  transpose() %>%
  simplify_all() %>%
  dplyr::as_data_frame()

get_property <- function(property, property_fun = function(x) x) {
    map_chr(fields, function(entry) {
      if (property %in% names(entry) && !is.null(entry[[property]]))
        property_fun(entry[[property]])
      else ""
    })
  }
  
process_options <- function(options) {
  if (class(options) == "list") {
    opts <- names(unlist(options, recursive = FALSE))
  } else {
    opts <- options
  }
  paste(map_chr(opts, ~sprintf("<code>%s</code>", .x)), collapse = ", ")
}

fields_data <- dplyr::data_frame(field = get_property("field"),
                          description = get_property("description"),
                          type = get_property("type"),
                          format = get_property("format"),
                          options = get_property("options", process_options),
                          required = get_property("required")) %>%
  tidyr::unite(`format/options`, format, options, sep = "") %>%
  split(.$required) %>%
  map(~.x %>% dplyr::select(-required))

make_datatable <- function(df) {
    DT::datatable(
      df,
      class = 'cell-border stripe',
      escape = FALSE,
      width = "100%",
      style = "bootstrap",
      rownames = FALSE,
      extensions = 'Buttons',
      options = list(scrollX = TRUE, autoWidth = TRUE, pageLength = 20
    ))
  }

req_table <- make_datatable(fields_data[["TRUE"]])
opt_table <- make_datatable(fields_data[["FALSE"]])
drv_table <- make_datatable(fields_derived)
              
```

##### **Required fields**
`r req_table`
<br/><br/>

##### **Optional fields**
`r opt_table`
<br/><br/>

##### **Derived fields**
`r drv_table`


### Export Data

#### Download the data
You can download the data from both the [home page](.) and the [visualization page](/app.html?id=visualization).

1. From the [home page](.)

    1.1. Click on the box corresponding to the domain you are interested in (e.g. Schizophrenia, Autism Spectrum Disorder, Hemisphere Damage).  
      
    1.2. Once you are on the page of the domain, click on the box corresponding to the meta-analysis you are interested in.
      
    1.3. In the data tab, click on the “Download” button. 
      
    1.4. Choose the data format that you want (EXCEL - recommended for manual calculations using a spreadsheet software - but you should make sure that your local spreadsheet software is set to use "." as decimal separator to avoid errors, or CSV - recommended for reading into a statistical software such as R) by clicking on it in the conditional menu. 
   
2. From the visualization page.
   
    2.1. Open the “Domain” drop-down menu and click on the one you are interested in.

    2.2. Open the “Dataset” drop-down menu and click on the meta-analysis you are interested in.

    2.3. Open the “Feature” drop-down menu and click on the feature you are interested in.  

    2.4. Click on the “Download data” button above the “Dataset” menu. This will download the data in CSV format. You can also click on “View raw dataset” and follow steps 1.2. and 1.3.  

3. From the documentation page.

    3.1. Open the “Datasets” tab and click on the dataset you are interested in.

    3.2. Click on the “Download data” button above the “Dataset” menu. You can also click on “View raw dataset” and follow steps 1.2. and 1.3. 

    3.3. Choose the data format that you want (EXCEL - recommended for manual calculations using a spreadsheet software - but you should make sure that your local spreadsheet software is set to use "." as decimal separator to avoid errors, or CSV - recommended for reading into a statistical software such as R) by clicking on it in the conditional menu. 
<br/><br/>

#### Open and work with the data
For a more detailed tutorial on how to open and work with the data in excel, see the [MetaLab Tutorial](http://metalab.stanford.edu/documentation/using_ma_data/).
In case you are encountering problems with opening the data in excel, you can also find troubleshooting of common issues on the [MetaLab Tutorial](http://metalab.stanford.edu/documentation/using_ma_data/). 
If you cannot find help there, you are also welcome to email one of the [team members](/about.html). 
<br/><br/>

#### Citations
Please cite publications linked to the dataset, as described in [Publications](/publications.html)


## {-}
```{r, echo=FALSE}
htmltools::includeHTML("footer.html")
```
