---
pagetitle: publications
---

```{r child='assets/setup.Rmd'}
```

```{r echo=FALSE}
menuNavbar()

#<div style="margin-left:200px; margin-right:200px; margin-top:30px; font-size:16px">

# </div>
# 
# <!--- "section" is ID of div containing tabs below -->
# <style>
# #section {
#   margin-left:200px;
#   margin-right:200px;
#   font-size:16px;
# }
# </style>
# 
# ## {.tabset .nav-tabs-custom}

```

<div style="margin-left:100px; margin-right:100px; margin-top:10px;">

# Publications

## {.tabset .nav-tabs-custom}

### Using MetaVoice Data

Researchers are allowed to use data available on the MetaVoice website. This can be in the form of citing meta-analytic results, or downloading dataset and conducting custom analyses. In both cases our citation policy is the following:

1. Researchers publishing or presenting work using data in MetaVoice must cite the publications linked to that dataset, as listed in the [Documentation](/documentation.html#datasets). (If there is no citation, then no citation for the individual dataset is necessary).

2. For referencing the use of MetaVoice, please also cite at least one of the following:    
    * REFERENCE 1
    * REFERENCE 2

3. If researchers use more than five datasets, we ask users as a courtesy to cite all data. But in case of severe space limitations, the MetaVoice database as a whole alone may be cited.

4. Since the MetaVoice site is continuously updated, we recommend that you list the date of download for your data in your manuscript. For example: "We analyze all data currently in MetaVoice (REFERENCE). Data were downloaded on 2020-11-01."

### Publications on MetaVoice


### Publications using MetaVoice


### Publications used for MetaVoice

#### MetaLab

This MetaVoice Website has been developed using the idea, code and structure of MetaLab. 

- Bergmann, C., Tsuji, S., Piccinini, P.E., Lewis, M.L., Braginsky, M., Frank, M.C., & Cristia, A. (2018). Promoting replicability in developmental research through meta-analyses: Insights from language acquisition research. *Child Development, 89*, 1996-2009 . DOI: 10.1111/cdev.13079 [[Repository]](https://osf.io/uhv3d/)
- Lewis, M. L., Braginsky, M., Tsuji, S., Bergmann, C., Piccinini, P. E., Cristia, A., & Frank, M. C. (2017/under review). A Quantitative Synthesis of Early Language Acquisition Using Meta-Analysis. DOI: 10.17605/OSF.IO/HTSJM [[Preprint]](http://psyarxiv.com/htsjm) 

#### Feature Descriptions

The feature descriptions used on the visualisations tool have been created based using the following papers:

- Fusaroli, R., Lambrechts, A., Bang, D., Bowler, D. M., & Gaigg, S. B. (2017). Is voice a marker for Autism spectrum disorder? A systematic review and meta‐analysis. Autism Research, 10(3), 384-407.
- Low, D. M., Bentley, K. H., & Ghosh, S. S. (2020). Automated assessment of psychiatric disorders using speech: A systematic review. Laryngoscope Investigative Otolaryngology, 5(1), 96-116.
- Mandal, M. K., Srivastava, P., & Singh, S. K. (1990). Paralinguistic characteristics of speech in schizophrenics and depressives. Journal of psychiatric research, 24(2), 191-196
- Wolfe, J. (2020). Formant: what is a formant?. Retrieved 9 November 2020, from http://newt.phys.unsw.edu.au/jw/formant.html
- Wood, S. (2005). What are formants?. Retrieved 9 November 2020, from https://person2.sol.lu.se/SidneyWood/praate/whatform.html




